### 2013-03-28 doc/sosp13/evaluation.tex
eval

Figure~\ref{fig:context-switch-exp} shows the average context switch time as
the number of workers grow. There are two important takeaway points from these
data. Context switch time for the number of workers we use ($\approx$1K workers) is
on the order of 50 ns; and prefetching has significant impact on context
switch time. And context switch time does not grow significantly with the
number of workers --- even with one-half million workers, context switch
is around 75ns. In comparison, for the same yield test using kernel-level
Pthreads on a single core, the switch time is 450ns for a few threads and 800ns for
1000-32000 threads.

>>>>

Figure~\ref{fig:context-switch-exp} shows the average context switch time as
the number of workers grow. There are two important takeaway points from these
data. Context switch time for the number of workers we use ($\approx$1K workers) is
on the order of 50 ns; and prefetching has significant impact on context
switch time. And context switch time does not grow significantly with the
number of workers --- even with one-half million workers, context
switch time is around 75ns. In comparison, for the same yield test using kernel-level
Pthreads on a single core, the switch time is 450ns for a few threads and 800ns for
1000-32000 threads.
